Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-15 paper/paper.tex
Fixed typos and corrected reference to proposition

We  need the  following proposition that  connects  liveness analysis  with
minefield semantics transitions. 
\begin{proposition}
\label{prop:correctness}
\begin{enumerate} 
\item Consider a \LET\ definition \linebreak $:\pi: (\LET~x
  \leftarrow~\ldots~\IN~e$, such that there is a use of $x$
  in $e$, i.e.  an occurrence of $\LET~y~\leftarrow~s~in
  \ldots$, where $s$ is $(\CAR\ x)$, $(\CDR\ x)$ or $(+\ x\ y)$, or
  $(\SIF\ x\ e1\ e2)$ or $(\SRETURN\ x)$. Then the demand on $x$ at $\pi$ is non-null. 
\item Assume that a  \LET\ definition $\pi: (\LET~z  \leftarrow~(\CONS~x~y)~\IN~e$ has an occurrence of 
 $(\CAR~z)$ in $e$. Then the liveness of $x$ at $\pi$ includes $\epsilon$.  Similarly if $e$ contains $(CDR~z)$, then the liveness of$y$ at $\pi$ includes $\epsilon$.  
\end{enumerate},
\end{proposition}

@@

\begin{proof}
For a program  executing according to {\em minefield  semantics}, if a
\bang\ has to  occur then some variable which is  dereferenced must be
set to  $\bot$, between its  creation and  use points.  This  can only
happen if  the liveness of  the variable being dereferenced  was null.
From  the lemma~\ref{lemma:no-calls-correctness}  it  is clear  that this  cannot
happen.
\end{proof}

For   a    programs   with   functions,   we    use   the   techniques
in~\cite{asati14lgc}. We  assume as  a contradiction that  the program
can enter a \bang\ state  and inline the  functions called to  obtain a
program that is without functions  but has the same execution behavior
and    demands    as   the    original    program.     We   then    use
Lemma~\ref{lemma:no-calls-correctness}  to  show  that  the  resulting
functionless program cannot enter a bang state.

>>>>

We  need the  following proposition that  connects  liveness analysis  with
minefield semantics transitions. 
\begin{proposition}
\label{prop:correctness}
\begin{enumerate} 
\item Consider a \LET\ definition \linebreak $:\pi: (\LET~x
  \leftarrow~\ldots~\IN~e$, such that there is a use of $x$
  in $e$, i.e.  an occurrence of $\LET~y~\leftarrow~s~in
  \ldots$, where $s$ is $(\CAR\ x)$, $(\CDR\ x)$ or $(+\ x\ y)$, or
  $(\SIF\ x\ e1\ e2)$ or $(\SRETURN\ x)$. Then the demand on $x$ at $\pi$ is non-null. 
\item Assume that a  \LET\ definition $\pi: (\LET~z  \leftarrow~(\CONS~x~y)~\IN~e$ has an occurrence of 
 $(\CAR~z)$ in $e$. Then the liveness of $x$ at $\pi$ includes $\epsilon$.  Similarly if $e$ contains $(\CDR~z)$, then the liveness of $y$ at $\pi$ includes $\epsilon$.  
\end{enumerate}
\end{proposition}

@@

\begin{proof}
For a program  executing according to {\em minefield  semantics}, if a
\bang\ has to  occur then some variable which is  dereferenced must be
set to  $\bot$, between its  creation and  use points.  This  can only
happen if  the liveness of  the variable being dereferenced  was null.
From  the Proposition~\ref{prop:correctness}  it  is clear  that this  cannot
happen.
\end{proof}

For   a    program   with   functions,   we    use   the   techniques
in~\cite{asati14lgc}. We  assume as  a contradiction that  the program
can enter a \bang\ state  and inline the  functions called to  obtain a
program that is without functions  but has the same execution behavior
and    demands    as   the    original    program.     We   then    use
Lemma~\ref{lemma:no-calls-correctness}  to  show  that  the  resulting
functionless program cannot enter a bang state.
